Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-07-07 bibat/examples/baseball/docs/report.qmd
Update baseball example

```{.python include="../baseball/data_preparation.py" start-line=103}
```

I had to update the `prepare_data` function to take into account the
two raw data sources:

>>>>

```{.python include="../baseball/data_preparation.py" start-line=77 end-line=161}
```

To take into account the inconsistency between the two raw data sources, I
first had to change the variable `RAW_DATA_FILES`:

```{.python include="../baseball/data_preparation.py" start-line=26 end-line=33}
```

Next I changed the `prepare_data` function to handle the two different data
sources.
